---
title: "Lab 1: Intro to R"
author: "Renee Wu"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

### Exercise 1

```{r view-girls-counts}
glimpse(arbuthnot)
arbuthnot$girls

```


### Exercise 2

There is an overall increase in the number of girls baptized, with a major dip between 1640-1660 as well as around 1704. 

```{r trend-girls}
# Insert code for Exercise 2 here
ggplot(data=arbuthnot,aes(x=year,y=girls))+
  geom_line()
```


### Exercise 3

The ratio of boys baptized fluctuates between 0.51 and 0.53 primarily, with some exceptions over the years. 

```{r plot-prop-boys-arbuthnot}
arbuthnot <- arbuthnot %>%
  mutate(total = boys + girls)

ggplot(data = arbuthnot, aes(x = year, y = total)) + 
  geom_line()

arbuthnot <- arbuthnot %>%
  mutate(boy_to_girl_ratio = boys / girls)

arbuthnot <- arbuthnot %>%
  mutate(boy_ratio = boys / total)

ggplot(data=arbuthnot,aes(x=year,y=boy_ratio))+
  geom_line()
```


### Exercise 4

The years 1940-2002 are included in this data set. The dimensions of it are 3 rows by 63 columns. The variables names are year, girls, and boys. 

```{r dim-present}
# Insert code for Exercise 4 here
glimpse(present)

```


### Exercise 5

They are of a similar magnitude, however, the arbuthnot data set has more variables. 

```{r count-compare}
# Insert code for Exercise 5 here
glimpse(arbuthnot)
```


### Exercise 6

Arbuthnot's observation about boys being born in greater proportion than girls holds true in the United States. The proportion of boys born is consistently around 0.512-0.514, however there has been a decrease in the proportion of boys born in more recent years. 

```{r plot-prop-boys-present}
# Insert code for Exercise 6 here
present <- present %>%
  mutate(total = boys + girls)

present <- present %>%
  mutate(boy_to_girl_ratio = boys / girls)

present <- present %>%
  mutate(boy_ratio = boys / total)

ggplot(data=present,aes(x=year,y=boy_ratio))+
  geom_line()
```


### Exercise 7

The United States had the most total number of births in 1961. 
```{r find-max-total}
# Insert code for Exercise 7 here
present%>%
  arrange(desc(total))
```

