---
title: "Lab 3: ggplot2"
author: "Renee Wu"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(ggplot2)
```

### Exercise 1

```{r}
housing <- read.csv("http://www.science.smith.edu/~jcrouser/SDS192/landdata-states.csv")
glimpse(housing)
hp2013Q1 <- housing %>%
  filter(Date == 2013.25)

ggplot(hp2013Q1, aes(y = Structure.Cost, x = Land.Value)) +
  geom_point()

home_value_plot<-ggplot(hp2013Q1, aes(y=Home.Value,x=Land.Value))+geom_point()+labs(x="Land Value", y="Home Value", title="2013 Q1 Home Values and Land Values")
```


### Exercise 2

```{r}
home_value_plot
```




### Exercise 3

It does not make sense to connect the observations with geom_line() in this case since line graphs imply a change over time. However, since the above plot is a the structure value as a function of the land value, there is no time variation. 



### Exercise 4
```{r}
home_value_plot<-home_value_plot+aes(color=Structure.Cost)
home_value_plot
```


### Exercise 5
```{r}
home_plot <- ggplot(housing, aes(y = State, x = Home.Price.Index)) + 
  geom_point(aes(color = Date),
             alpha = 0.3,
             size = 1.5,
             position = position_jitter(width = 0, height = 0.25))

home_plot <- home_plot + 
  scale_y_discrete(name = "State Abbreviation")

home_plot + 
  scale_color_continuous(breaks = c(1975.25, 1994.25, 2013.25),
                         labels = c(1971, 1994, 2013))

home_plot <- home_plot +
  scale_color_continuous(breaks = c(1975.25, 1994.25, 2013.25),
                         labels = c(1971, 1994, 2013),
                         low = "blue", high = "red")
home_plot<-home_plot+geom_vline(xintercept = 1, linetype="dashed")
home_plot
```



### Exercise 6

To place the dotted vertical line behind the previous dotted values, apply the geom_vline() function prior to the geom_point() layer. 


### Exercise 7

The following is a plot of home prices faceted by region. 

```{r}
housing%>%
  drop_na(region)%>%
  ggplot(aes(x=Date,y=Home.Value))+
  geom_line()+
  labs(y="Home Value", title="Home Values by Region from 1975-2013")
  facet_wrap(~region,ncol=10)

```



