---
title: "Lab 5"
author: "Renee Wu"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)

```

### Exercise 1

```{r}
library(babynames)

head(babynames)

babynames%>%
  select(year,name,n)%>%
  head()

babynames%>%
  filter(name=="Bella")%>%
  head()

bella<-babynames%>%
  filter(name=="Bella")%>%
  select(year,name,sex,n)

dim(bella)
head(bella)
class(bella)

ggplot(data=bella,aes(x=year,y=n))+
  geom_line(aes(color=sex))

babynames<-babynames%>%
  mutate(popular=prop>0.01)

popular<-babynames%>%
  filter(is_popular)

nrow(popular)
head(popular)
popular%>%
  arrange(desc(prop))
```
The prop variable represented the number of babies with that name divided by total number of babies in that year. 

### Exercise 2

```{r}
babynames%>%
  filter(name=="John")%>%
  arrange(desc(prop))
```

The name John was used most frequently in 1880. 

### Exercise 3

```{r}
babynames%>%
  filter(year==1880)%>%
  arrange(desc(prop))
```

John was the most popular name in 1880. 

### Exercise 4

In order to find the year in which a name given to male and female babies are about equal, use the summarize() function to subtract the proportion of the total for each sex and arrange by ascending order. 

### Exercise 5
```{r}
bella%>%
  summarize(most_bellas=max(n))

bella%>%
  summarize(num_rows=n(),most_bellas=max(n))
```
The value of num_rows represents the years that were accounted for within finding the year in which the most Bellas were born. 

### Exercise 6
```{r}
babynames%>%
  filter(name=="Jordan")%>%
  select(-name)%>%
  arrange(desc(prop))
```

